\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{bm}
\usepackage{setspace}
\usepackage[inline,shortlabels]{enumitem}
\usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\colorlet{deepblue}{blue!70!black}
\colorlet{brickred}{red!60!black}
\colorlet{envgray}{black!70}
\colorlet{mutedorange}{orange!40!black}
\colorlet{accentcolor}{purple!65!black}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{supertabular}
\usepackage{mathrsfs}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepgfplotslibrary{fillbetween}
\usepackage[expansion=false]{microtype}
\usepackage{titling}
\usepackage{csquotes}
\usepackage[round]{natbib}
\bibliographystyle{aer}
\usepackage{doi}
\usepackage{hyperref}
\usepackage[capitalise]{cleveref}
\usetikzlibrary{patterns}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}
\newcommand{\Appref}[1]{\hyperref[#1]{Appendix \ref*{#1}}}
\newcommand{\ProofOf}[1]{Proof of \texorpdfstring{\Cref{#1}}{\detokenize{#1}}}
\newtheoremstyle{break}
  {}{}% Space above/below
  {\itshape}{}% Body font, indent
  {\bfseries}{}% Head font, punctuation
  {\newline}{}% Space after head = newline
\theoremstyle{break}
\newtheorem{assumption}{Assumption}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem*{algorithm*}{Algorithm}
\newtheorem{theorem}{Theorem}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{proposition*}{Proposition}
\newtheorem{observation}{Observation}
\crefname{assumption}{assumption}{assumptions}
\Crefname{assumption}{Assumption}{Assumptions}


%---------------------------------------------------------------------
\title{Robust Narrative Persuasion}
\author{Song Li\\[0.5em]
}
% \small Supervisor: Fernando Payr\'o\\
% \small Co-supervisor: Antoine Zerbini}
\date{\today}
%---------------------------------------------------------------------
\begin{document}
\maketitle

\begin{abstract}
This paper studies a sender who designs a public menu of narratives for a heterogeneous population whose cross-sectional distribution of priors is known only through moment restrictions. After observing a public event, each receiver selects the narrative that best fits his prior and updates within it. We show that under binary states, one threshold-setting narrative per realization suffices. Implementability is bounded by a persuasion frontier, along which there is a trade-off across signal realizations. In a political-narrative application, the dictator's optimal value can fall as the average prior rises: a higher average prior can let Nature meet the variance lower bound with less mass strictly above the persuasion threshold.

\end{abstract}

\noindent\textbf{JEL Classification:} D82; D83; D81; C72.

\noindent\textbf{Keywords:} Persuasion; Narratives; Robustness; Ambiguity.

\vspace{0.75em}
\noindent\textbf{Acknowledgments:}
I am especially grateful to Fernando Payr\'{o} for invaluable guidance and generous support throughout this project. I also thank Antoine Zerbini for valuable feedback and discussions.

\section{Introduction}
%Fer: TBW
\input{texs/introduction}
% \subsection{Motivating Examples}
% \input{texs/example}
%Fer TBW
% \subsection{Literature Review}
%Fer: This guy came to mind when thinking about this proyect work (Alexei Parakhonyak)
%Fer: Also Jian Li, Peter Klibanoff and Xiaoyu Cheng and have papers on persuasion under ambiguity. Cuimin Ba also has a related paper
\section{Model}
\label{sec:model}
% \subsection{Primitives}
% %Fer: Write here all the ingredients of the model. Dont assume binary yet.
% \subsection{Narratives}
% %Fer: Write here the version of the model without ambiguity.
% \subsection{Ambiguity}
% %Fer: Add here the ambiguity in general. Then explain how unrestricted ambiguity can lead to non rubust mechanisms (Ball's paper) and thus, you consider moment restrictions (Ball's result). Give examples of moment restrictions. We shhould look in the literature as to when they arise (should be easy, Francesca Molinary has a book about it).

\input{texs/model}

\section{Results}
\label{sec:results}
Every signal realization generates one persuasion threshold. Since the state space is binary and each receiver has state-matching preference, narrative selection and action choice are cutoff-based: after each $s\in S$, the menu separates types at a threshold $\theta_s$, distinguishing those who take the sender-preferred action from those who do not. Thus a menu matters for payoffs only through the threshold profile $(\theta_s)_{s\in S}$. The main results characterize this profile: one threshold-setting narrative per realization is enough, implementability is described by odds-coordinate halfspaces, and the robust inner problem is solved for the induced threshold payoff.

\subsection{Benchmark}
\label{sec:benchmark}
%Fer: Write here the benchmark result (no ambiguity). This is still a result as it generalizes Aina.
\input{texs/benchmark}
\subsection{Robustness}
\label{sec:robustness}
%Fer: Write here the results. The current order is fine
\input{texs/robustness}
%\input{texs/extension}
\subsection{Discussion}
\label{sec:discussion}
\input{texs/discussion}
\section{Application}
%Fer: TBW
\input{texs/application}
\input{texs/conclusion}
\clearpage
\appendix
\renewcommand{\thesection}{\Alph{section}}
\newcommand{\theappendix}{\Alph{section}}
\renewcommand{\thesubsection}{\Alph{section}.\arabic{subsection}}
% \input{texs/appendix}
\renewcommand{\theequation}{\theappendix.\arabic{equation}}
\renewcommand{\thefigure}{\theappendix.\arabic{figure}}
\renewcommand{\thetable}{\theappendix.\arabic{table}}
\renewcommand{\thetheorem}{\theappendix.\arabic{theorem}}
\renewcommand{\theproposition}{\theappendix.\arabic{proposition}}
\renewcommand{\thelemma}{\theappendix.\arabic{lemma}}
\renewcommand{\thecorollary}{\theappendix.\arabic{corollary}}
\renewcommand{\thedefinition}{\theappendix.\arabic{definition}}
\renewcommand{\theremark}{\theappendix.\arabic{remark}}
\renewcommand{\theassumption}{\theappendix.\arabic{assumption}}
\renewcommand{\theexample}{\theappendix.\arabic{example}}
\renewcommand{\theobservation}{\theappendix.\arabic{observation}}
\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{theorem}{0}
\setcounter{proposition}{0}
\setcounter{lemma}{0}
\setcounter{corollary}{0}
\setcounter{definition}{0}
\setcounter{remark}{0}
\setcounter{assumption}{0}
\setcounter{example}{0}
\setcounter{observation}{0}
\makeatletter
\@addtoreset{equation}{section}
\@addtoreset{figure}{section}
\@addtoreset{table}{section}
\@addtoreset{theorem}{section}
\@addtoreset{proposition}{section}
\@addtoreset{lemma}{section}
\@addtoreset{corollary}{section}
\@addtoreset{definition}{section}
\@addtoreset{remark}{section}
\@addtoreset{assumption}{section}
\@addtoreset{example}{section}
\@addtoreset{observation}{section}
\makeatother
%Fer: Write here all the mathematical preliminaries you need
\input{texs/appendix}
\clearpage
\begingroup
% \footnotesize
\bibliography{refs}
\endgroup
\end{document}
